Performance of prediction models for opportunities for improvment in trauma care among women compared to men and across patient cohorts

### 2023-12-08 manuscript.Rmd
Comment on manuscript

@@

@@

@@

Karolinska trauma registry contains 11864 patients, of which 6310 are reviewed for OFI, either through selection by individual review or application of audit filters, as well as an unknown process (n=2). Through this, 1316 patients were selected for the morbidity conference, and 596 patients for the mortality conference. Out of 596 deaths reviewed, 35 were found to be preventable (n=4) or possibly preventable (n=31). The remaining 561 patients were thus rendered non-preventable without OFI. Further, 1316 alive patients were included during a morbidity conference, of which 396 (7%) were identified as cases with OFI.

>>>>

<!-- Expand on this section to introduce AI/ML in trauma care more generally, and then focus on the application of ML to select patients for M&M -->

@@

<!-- Similar performance across different subgroups is also important from a fairness perspective, meaning that if the model performs worse among women, then we risk providing lower quality care to women, because we might miss important OFI -->

@@

<!-- Consider citing Hussein's paper in your definition of OFI: "The outcome was the presence of OFI, as decided by the morbidity and mortality conference. An OFI is any failure of care including, but not limited to, any potentially preventable or preventable death, delay in treatment, clinical judgment error, missed diagnosis and technical error as decided by the mortality and morbidity conference. The study outcome is binary with the levels “Yes - At least one OFI identified” and “No - No OFI identified”."

https://sjtrem.biomedcentral.com/articles/10.1186/s13049-023-01157-y

-->

@@

The Karolinska trauma registry contains 11864 patients, of which 6310 are reviewed for OFI, either through selection by individual review or application of audit filters, as well as an unknown process (n=2). Through this, 1316 patients were selected for the morbidity conference, and 596 patients for the mortality conference. Out of 596 deaths reviewed, 35 were found to be preventable (n=4) or possibly preventable (n=31). The remaining 561 patients were thus rendered non-preventable without OFI. Further, 1316 alive patients were included during a morbidity conference, of which 396 (7%) were identified as cases with OFI.
